\Large\textbf{Decentralized Data Marketplace to Enable Trusted Machine Economy}

### 2019-09-09 paper.tex
Remove redundant words

\subsection{Participants Registration}
At the beginning, the registrar creates a Registration Contract (Figure \ref{fig:registration_contract}), which maintains all participants' information, including their DID (Decentralized Identifiers) Documents and public keys. Only one Registration Contract is needed, and everyone can query the participants' public keys. Then some trustworthy brokers who pass procedures for conformity assessment are added to the decentralized data marketplace. Anyone who would like to sell or purchase data may register to become the data providers or consumers. The registrar has the authority to agree with applications. After that, their identities are available in the Registration Contract and launching and trading processes can be started.

>>>>

\subsection{Participants Registration}
At the beginning, the registrar creates a Registration Contract, which maintains all participants' information, including their DID (Decentralized Identifiers) Documents and public keys. Only one Registration Contract is needed, and everyone can query the participants' public keys. Then some trustworthy brokers who pass procedures for conformity assessment are added to the decentralized data marketplace. Anyone who would like to sell or purchase data may register to become the data providers or consumers. The registrar has the authority to agree with applications. After that, their identities are available in the Registration Contract and launching and trading processes can be started.
